\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-25 paper.qmd
Figure 17 initial figure title

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 10
#| fig-width: 10
#| fig-cap: "Model in \\gD{}, on the tSNE layout (a), and three views (b, c, d) of the fit in projections from $10\\text{-}D$, for the digit 1 of MNIST data ($a_1 = 0.07$, $b = 456 \\  (19, \ 24)$, $m = 226$, and benchmark value to remove large edges is $0.114$). (b) The non-linear structure observed in the \\gD{} layout of tSNE (@fig-tsne-best) is also visible when visualizing the model overlaid on the data space. This indicates that tSNE accurately captures the non-linear structure of the $10\\text{-}D$ data. (c) the model shows a twisted pattern within the non-linear structure in $10\\text{-}D$ space, which is an additional pattern not visible in the \\gD{} representation (@fig-tsne-best). (d) some long edges exist in the $10\\text{-}D$ space that are not recognized as long edges in the \\gD{} representation. The full video is available at <https://youtu.be/zcg_GXBmqjA>."

>>>>

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 10
#| fig-width: 10
#| fig-cap: "Model in \\gD{}, on the layout a and three views of the fit in projections from $10\\text{-}D$, for the MNIST digit 1 data ($n =  7877$ and $p = 10$)."

### 2024-09-25 paper.tex
Figure 17 initial figure title

\caption{\label{fig-mnist-tri-proj}Model in \gD{}, on the tSNE layout
(a), and three views (b, c, d) of the fit in projections from
\(10\text{-}D\), for the digit 1 of MNIST data (\(a_1 = 0.07\),
\(b = 456 \  (19,  24)\), \(m = 226\), and benchmark value to remove
large edges is \(0.114\)). (b) The non-linear structure observed in the
\gD{} layout of tSNE (\textbf{?@fig-tsne-best}) is also visible when
visualizing the model overlaid on the data space. This indicates that
tSNE accurately captures the non-linear structure of the \(10\text{-}D\)
data. (c) the model shows a twisted pattern within the non-linear
structure in \(10\text{-}D\) space, which is an additional pattern not
visible in the \gD{} representation (\textbf{?@fig-tsne-best}). (d) some
long edges exist in the \(10\text{-}D\) space that are not recognized as
long edges in the \gD{} representation. The full video is available at
\url{https://youtu.be/zcg_GXBmqjA}.}

>>>>

\caption{\label{fig-mnist-tri-proj}Model in \gD{}, on the layout a and
three views of the fit in projections from \(10\text{-}D\), for the
MNIST digit 1 data (\(n =  7877\) and \(p = 10\)).}
